---
title: "Health Data Analysis"
author: "Arron Lacey"
date: "2024-12-09"
output: html
---

# Health Data Viz Analysis
Test Quarto works by typing this text (and then run the document)


## Load necessary libraries

Here we load all of the libraries we will need. To avoid installing libraries repeatedly, it is best to install them in a separate R session. Or install in the code cell and the comment out
```{r}
# install.packages("GGally")
library(tidyverse)
library(GGally)
library(readr)
library(NHANES)
```


### Load in the NHANES Data


```{r}
# Select the relevant columns from the NHANES dataset
health_data <- NHANES %>% select(BMI, Age, Gender, TotChol)
summary(health_data)
```

## Plot a histogram of BMI

```{r}
# Create a histogram of BMI using ggplot
ggplot(health_data, aes(x = BMI)) +
  geom_histogram(binwidth = 1, fill = "skyblue", colour = "black") +
  labs(title = "Distribution of BMI") +
  theme_minimal()
```

Look at this handy guide to [Quarto](https://quarto.org/docs/guide)
